 Casting multiple shadows: interactive data visualisation with tours and embeddings

### 2020-02-07 paper.Rmd
restructure as html doc; reclassify structure

---
title: " Casting multiple shadows: interactive data visualisation with tours and embeddings"
author:
  - name: Stuart Lee
    affiliation: Monash University
  - name: Di Cook
    affiliation: Monash University
date: "`r Sys.Date()`"
output: distill::distill_article
bibliography: liminal.bib
---

@@

<!--
- review of embedding algorithms, interactive graphics, tours
- technology
- design
- examples/benchmarks
  - Kevin moon
  - pdfsense
  - single cell
  - quick draw
-->

@@

# Methods

@@

# Results

>>>>

---
title: " Casting multiple shadows: interactive data visualisation with tours and embeddings"
author:
  - name: Stuart Lee
  - name: Di Cook
date: "`r Sys.Date()`"
output: bookdown::html_document2
bibliography: liminal.bib
---

@@

<!--
- review of embedding algorithms, interactive graphics, tours
- technology
- design
- examples/benchmarks
  - Kevin moon
  - pdfsense
  - single cell
  - quick draw

-->

@@

# Design

@@

# Implementation

The `liminal` software is implemented as an open source R package @baseR. All 
visualisations produced by the package were constructed using the `vegawidget`
package, which is  an R interface to the Vega-Lite grammar of interactive graphics. Ensemble graphics for arranging tour and embedding views 
are generated using the `shiny` packages. We have made extensive use of the 
`tourr` package for constructing tour paths.

## Interactivity for embedding exploration

# Case Studies
